---
title: "Final Report for Intro to Data Science"
output:
   html_notebook:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
---
Victoria Cinquepalmi and Maggie Julian

video- https://web.microsoftstream.com/video/654e7ac4-22ae-4e57-a4fa-74fd3fbfe30f 

slides- https://docs.google.com/presentation/d/1S-nmrpwXVyLgNh-qzCdaE22Q1fuqSNrvpMtZkDpLDUY/edit#slide=id.gc6f9e470d_0_0 

# Introduction

The data set we chose was the billboard top 100 from 2015. We collected this data from Professor Sanchez-Arias Github. 

|The Variables    | What they do                          |
|-----------------|---------------------------------------|
| Rank            | Shows the rank from 1 to 100          |
| Song            | Shows the song title                  |
| Artist          | Shows the name of the singer(s)       |
| Year            | Shows the year of the songs release   |
| Lyrics          | Shows the lyrics of the song          | 

The packages we used are the `tidyverse` and `ggplot2`

We are going to be pulling apart Billboard's top 100 from 2015 to find out:

- Does having someone featured have an effect on how well the song ranks?
- Do songs that contain certain words rank higher?


### Loading the `tidyverse` 

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
```


### Loading the `dataset`

This is the data set for all of the summer hits from 2015

```{r}
summer_hits_URL <- "https://raw.githubusercontent.com/reisanar/datasets/master/BB_top100_2015.csv"
summer_hits <- read.csv(summer_hits_URL)
summer_hits
```



### Loading `ggplot2`

```{r}
library(ggplot2)
```





# Question 1

### How well do songs that have featured  artists rank?

We wanted to answer this question to find out if songs that have extra Artists featured on them tend to rank higher on the billboard top 100. 

Filtering the data:

We want to filter the data to show only the songs that contain featuring artists on them. 

```{r}
featured <- summer_hits %>%
  filter(str_detect(Artist,"featuring"))
featured
```
The table above presents songs, made in the summer of 2015, that had another artist featured on it. 


Making the graph:

```{r}
featured %>% 
  ggplot(aes(x = Rank)) +
  geom_histogram(binwidth = 5, color = "black", fill = "pink") +
  labs(title = "Rank of Songs Containing Featured Artists", x = "Rank of song (out of 100)", y = "Count of Songs")
```

As you can see on the graph above, the range of ranks that featured the most amount of artists were at 25, 45, and 75. This graph is showing that there probably was not an correlation between how well the song ranked, weather or not the song had someone featured on it. 



# Question 2

### How many songs say baby in the lyrics?

We wanted to answer this question because a common critique about modern music is how it repeatedly says the word baby, and we wanted to find out if that's true. 


The code below is creating another column of data that is figuring out whether or not that a song contains the lyric "baby"


```{r}
has_baby <- summer_hits %>% 
  mutate(
      contains_baby = case_when(
      str_detect(Lyrics, "baby") ~ "yes", 
      TRUE ~ "No"))
has_baby
```


Making the graphs:

```{r}
ggplot(has_baby) +
  geom_col(aes(x = contains_baby, y = 1, color = contains_baby)) +
  labs(title = "Songs Containing 'baby' VS the Songs that Don't", x = "Lyrics", y = "Number of Songs")
```

The graph above is showing that there is the exact same number of songs that have the lyric baby. 


Pulling the data:

```{r}
has_baby %>% 
  filter(contains_baby == "yes")
```
The dataset above is showing a decently even dispursement of songs that contain the word baby. 


The code below is creating another column of data that is figuring out whether or not that a song contains the lyric "girl"

```{r}
has_girl <- summer_hits %>% 
  mutate(
    contains_girl = case_when(
      str_detect(Lyrics, "girl") ~ "yes", 
      TRUE ~ "No"
    )
  ) 
has_girl
```

Making the graph:

```{r}
ggplot(has_girl) +
  geom_col(aes(x = contains_girl, y = 1, color = contains_girl)) +
  labs(title = "Songs Containing 'girl' VS the Songs that Don't", x = "Lyrics", y = "Number of Songs")
```

The graph above shows that there are 42 songs  containg the lyric "girl"

Pulling the data:

```{r}
has_girl %>% 
  filter(contains_girl == "yes")
```
The data set above shows a pretty even disbursement of songs that contain the lyric "baby" 



The code below is creating another column of data that is figuring out whether or not that a song contains the lyric "boy"

```{r}
has_boy <- summer_hits %>% 
  mutate(
    contains_boy = case_when(
      str_detect(Lyrics, "Boy") ~ "yes", 
      TRUE ~ "No"
    )
  ) 
has_boy
```

Creating the graph:

```{r}
ggplot(has_boy) +
  geom_col(aes(x = contains_boy, y = 1, color = contains_boy)) +
  labs(title = "Songs Containing 'boy' VS the Songs that Don't", x = "Lyrics", y = "Number of Songs")
```
The graph above is showing that not a single song in the list contains the lyric "boy"




# Conclusion

We have found out that it doesn’t matter what type of song you make you have at about the same chance of being in the top 100. We came to this conclusion because, the data we have presented has shown it does a small effect if an artist includes lyrics like "girl or "baby" collaborates with others or if they use words like “baby” to make their song rise to the top. It truly depends on what the people like most at the moment. 


