---
title: "Final Report for Intro to Data Science"
output: html_notebook
---

This is where the final project report write-up goes. 


Before you submit, make sure everything runs as expected.

You can add sections as you see fit. Make sure you have a section called "Introduction" at the beginning and a section called "Conclusion" at the end. The rest is up to you!

_Make use of your knowledge of Markdown to appropriately typeset this report!_

# Introduction

We are going to be pulling apart Billboard's top 100 from 2015 to find out:

- How many songs have people featured?
- How many songs say baby or in the lyrics?


### Loading the `tidyverse` 

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
```


### Loading the `dataset`

This is the data set for all of the summer hits from 2015

```{r}
summer_hits_URL <- "https://raw.githubusercontent.com/reisanar/datasets/master/BB_top100_2015.csv"
summer_hits <- read.csv(summer_hits_URL)
summer_hits
```



### Loading `ggplot2`

```{r}
library(ggplot2)
```





## Question 1

### How well do songs that have featured  artists rank?

We wanted to answer this question to find out if songs that have extra Artists featured on them tend to rank higher on the billboard top 100. 

Filtering the data:

We want to filter the data to show only the songs that contain featuring artists on them. 

```{r}
featured <- summer_hits %>%
  filter(str_detect(Artist,"featuring"))
featured
```
The table above presents songs, made in the summer of 2015, that had another artist featured on it. 


Making the graph:

```{r}
featured %>% 
  ggplot(aes(x = Rank)) +
  geom_histogram(binwidth = 5, color = "black", fill = "pink") +
  labs(title = "Rank of Songs Containing Featured Artists", x = "Rank of song (out of 100)", y = "Count of Songs")
```

As you can see on the graph above, the range of ranks that featured the most amount of artists were at 25, 45, and 75. This graph is showing that there probably was not an correlation between how well the song ranked, weather or not the song had someone featured on it. 



## Question 2

### How many songs say baby in the lyrics?


We wanted to answer this question because a common critique about modern music is how it repeatedly says the word baby, and we wanted to find out if that's true. 


The code below is createing another colum of data that is figuring out wheather or not that a song contains the lyric "baby"

```{r}
has_baby <- summer_hits %>% 
  mutate(
    contains_baby = case_when(
      str_detect(Lyrics, "baby") ~ "yes", 
      TRUE ~ "No"
    )
  ) 
has_baby
```

```{r}
filter(has_baby, contains_baby == "yes")
```


```{r}
ggplot(has_baby) +
  geom_col(aes(x = contains_baby, y = 1, color = contains_baby)) +
  labs(title = "Songs Containing 'baby' VS the Songs that Don't", x = "Lyrics", y = "Number of Songs")
```


```{r}
bb <- summer_hits %>%
  filter(str_detect(Lyrics, "baby")) %>%
  ggplot() +
  geom_col(aes(x = "Lyrics", y = .6, fill = str_detect(Lyrics, "baby"))) +
  labs(title = "Songs Containing 'baby' VS the Songs that Don't", x = "Lyrics", y = "Number of Songs")
bb
  
```

























