---
title: "Final Report for Intro to Data Science"
output: html_notebook
---

This is where the final project report write-up goes. 


Before you submit, make sure everything runs as expected.

You can add sections as you see fit. Make sure you have a section called "Introduction" at the beginning and a section called "Conclusion" at the end. The rest is up to you!

_Make use of your knowledge of Markdown to appropriately typeset this report!_

# Introduction

We are going to be pulling apart Billboard's top 100 from 2015 to find out:

- How many songs have people featured?
- How many songs say baby or a similar word in the lyrics?


### Loading the `tidyverse` 

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
```


### Loading the `datasets`

This is the data set for all of the summer hits from 2015

```{r}
summer_hits_URL <- "https://raw.githubusercontent.com/reisanar/datasets/master/BB_top100_2015.csv"
summer_hits <- read.csv(summer_hits_URL)
summer_hits
```


This is the data set for the Billboard top hits from 1960 to 2016

```{r}
billboard_top_hits_long <- "https://raw.githubusercontent.com/reisanar/datasets/e74de9e16227527da1f12208db89fe82188269fb/bbTop100.csv"
bb_extra_info <- read.csv(billboard_top_hits_long)
bb_extra_info
```

Filtering to data to just 2015

```{r}
bb2015 <- bb_extra_info %>% 
  filter(year == 2015) 
bb2015
```

### Loading `ggplot2`

```{r}
library(ggplot2)
```










```{r}
names(bb2015)[names(bb2015) == 'artist_name'] <- 'Artist'
```

Merging the two data sets 

```{r}
new_data <- full_join(summer_hits, bb2015, by = "Artist")
new_data
```


## Question 1

### How well do songs that have featured  artists rank?

We wanted to answer this question to find out if songs that have people featured on them tend to score higher on the billboard top 100. 

Filtering the data:

```{r}
featured <- new_data %>%
  filter(str_detect(Artist,"featuring"))
featured
```
As you can see in the table above the number one song of summer 2015had someone featured on it. 


Making the graph:

```{r}
featured %>% 
  ggplot(aes(x = Rank)) +
  geom_histogram(binwidth = 5, color = "black", fill = "pink") +
  labs(title = "Rank of Songs Containing Featured Artists", x = "Rank of song (out of 100)", y = "Count of Songs")
```

As you can see on the graph above, the range of ranks that featured the most amount of people were at 25, 45, and 75. This graph is showing that there probably was not an correlation between how well the song ranked, and weather or not the song had someone featured




```{r}
new_data %>%
   filter(str_detect(Lyrics,"baby"))
  
```






















