---
title: "Final Report for Intro to Data Science"
output: html_notebook
---

This is where the final project report write-up goes. 


Before you submit, make sure everything runs as expected.

You can add sections as you see fit. Make sure you have a section called "Introduction" at the beginning and a section called "Conclusion" at the end. The rest is up to you!

_Make use of your knowledge of Markdown to appropriately typeset this report!_


```{r, message=FALSE, warning=FALSE}
library(tidyverse)
```


## Loading the data

load the `datasets`

```{r}
summer_hits_URL <- "https://raw.githubusercontent.com/reisanar/datasets/master/BB_top100_2015.csv"
summer_hits <- read.csv(summer_hits_URL)
summer_hits
```

```{r}
billboard_top_hits_long <- "https://raw.githubusercontent.com/reisanar/datasets/e74de9e16227527da1f12208db89fe82188269fb/bbTop100.csv"
bb_extra_info <- read.csv(billboard_top_hits_long)
bb_extra_info
```


```{r}
bb2015 <- bb_extra_info %>% 
  filter(year == 2015) 
bb2015
```

```{r}
names(bb2015)[names(bb2015) == 'artist_name'] <- 'Artist'
```


```{r}
new_data <- full_join(summer_hits, bb2015, by = "Artist")
new_data
```


```{r}
new_data %>%
  filter(str_detect(Artist,"featuring"))
```





